Towards Transparency and Open Science

### 2023-07-21 manuscript.Rmd
a few more punctations in formula
add author

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    includes:
      in_header: "preamble.tex"
    latex_engine: "lualatex"
    toc: true
    number_sections: false
    keep_tex:  true
fontsize: 11pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
# asymetric geometry is set after/in frontmatter.md
geometry: "left=4cm, right=4cm, top=3cm, bottom=5cm, bindingoffset=7mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}\\\\textsc{Abstract:}', readLines('abstract.md'), '\\\\vspace{1mm}\\\\par \\\\textsc{Zusammenfassung:}\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  packages:
    - gert
    - aaronpeikert/repro@5075336
  files:
    - zusammenfassung.md
    - abstract.md
    - frontmatter.md
    - cover.pdf
    - preamble.tex
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
    - lualatex-math
    - luatexbase
    - titling
  apt:
    - git
    - rsync
---

@@

The inference goal for comparing other theories to $g(x)$ is, therefore:
\begin{equation}
\mathbb{E}_{X \sim f}\left[\log(g(x|\theta_*))\right]
\end{equation}
Of course, we usually do not know $\theta_*$.
That is why it is necessary to induce it from data, denoted as $\hat\theta(y)$, where $Y$ are $n$ independent samples from $X\sim f$.

@@

That is to say, any induced estimate will be suboptimal.
The inference goal, however, is to compare the theory $g$ to reality $f$, not to evaluate the estimates of $\hat\theta$.
The point is to make a statement about the theory, not to make a statement about the data in light of the theory.
If the estimate of $\hat\theta(y)$, i.e., the inductive process, is unbiased in the sense that it converges towards $\theta_*$, we may form an expectation over the data $Y$:
\begin{equation}
\mathbb{E}_{Y \sim f^n}\mathbb{E}_{X \sim f}[\log(g(x|\hat\theta(y)))]\label{eq:dataexp}
\end{equation}

@@

As stated earlier, using cross-validation, it is possible to estimate \linebreak[4] $\mathbb{E}_{X \sim f}\mathbb{E}_{Y \sim f^n}[log(g(x|\hat\theta(y)))]$ as well; this connects the information-theoretic setup with this approach [@stoneAsymptoticEquivalenceChoice1977; @stoneCrossValidatoryChoiceAssessment1974].
To make the link to the first approach even more clear, we may give an alternative definition of complexity as the expected difference between observed prediction error and expected prediction error [@hauensteinComputingAICBlackbox2018]:
\begin{equation}
\mathcal{C} = \frac{1}{n} \sum_{i=1}^{n}L(y_i, g(y_i|\hat\theta(y_{-i}))) - L(y_i, g(y_i|\hat\theta(y)))
\end{equation}

Instead of a formal analysis to derive $\mathcal{C}$, we can simply repeat the inductive process, i.e., use cross-validation.
The former requires the derivatives with regard to the parameters, so I call it parametric estimator of complexity.
The latter eschews the need for that, so I call it non-parametric estimator of complexity.
Only requiring that a process can be repeated on other data drastically expands the set of inductive processes for which we can estimate the inductive bias.

>>>>

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
author: "Aaron Peikert"
output:
  bookdown::pdf_document2:
    includes:
      in_header: "preamble.tex"
    latex_engine: "lualatex"
    toc: true
    number_sections: false
    keep_tex:  true
fontsize: 11pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
# asymetric geometry is set after/in frontmatter.md
geometry: "left=4cm, right=4cm, top=3cm, bottom=5cm, bindingoffset=7mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}\\\\textsc{Abstract:}', readLines('abstract.md'), '\\\\vspace{1mm}\\\\par \\\\textsc{Zusammenfassung:}\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  packages:
    - gert
    - aaronpeikert/repro@5075336
  files:
    - zusammenfassung.md
    - abstract.md
    - frontmatter.md
    - cover.pdf
    - preamble.tex
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
    - lualatex-math
    - luatexbase
    - titling
  apt:
    - git
    - rsync
---

@@

The inference goal for comparing other theories to $g(x)$ is, therefore:
\begin{equation}
\mathbb{E}_{X \sim f}\left[\log(g(x|\theta_*))\right]\,.
\end{equation}
Of course, we usually do not know $\theta_*$.
That is why it is necessary to induce it from data, denoted as $\hat\theta(y)$, where $Y$ are $n$ independent samples from $X\sim f$.

@@

That is to say, any induced estimate will be suboptimal.
The inference goal, however, is to compare the theory $g$ to reality $f$, not to evaluate the estimates of $\hat\theta$.
The point is to make a statement about the theory, not to make a statement about the data in light of the theory.
If the estimate of $\hat\theta(y)$, i.e., the inductive process, is unbiased in the sense that it converges towards $\theta_*$, we may form an expectation over the data $Y$:
\begin{equation}
\mathbb{E}_{Y \sim f^n}\mathbb{E}_{X \sim f}[\log(g(x|\hat\theta(y)))]\label{eq:dataexp}\,.
\end{equation}

@@

As stated earlier, using cross-validation, it is possible to estimate \linebreak[4] $\mathbb{E}_{X \sim f}\mathbb{E}_{Y \sim f^n}[log(g(x|\hat\theta(y)))]$ as well; this connects the information-theoretic setup with this approach [@stoneAsymptoticEquivalenceChoice1977; @stoneCrossValidatoryChoiceAssessment1974].
To make the link to the first approach even more clear, we may give an alternative definition of complexity as the expected difference between observed prediction error and expected prediction error [@hauensteinComputingAICBlackbox2018]:
\begin{equation}
\mathcal{C} = \frac{1}{n} \sum_{i=1}^{n}L(y_i, g(y_i|\hat\theta(y_{-i}))) - L(y_i, g(y_i|\hat\theta(y)))
\end{equation}
Instead of a formal analysis to derive $\mathcal{C}$, we can simply repeat the inductive process, i.e., use cross-validation.
The former requires the derivatives with regard to the parameters, so I call it parametric estimator of complexity.
The latter eschews the need for that, so I call it non-parametric estimator of complexity.
Only requiring that a process can be repeated on other data drastically expands the set of inductive processes for which we can estimate the inductive bias.
